Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-07 papers/termination/paper.tex
nudge bib

\title{Synthesising Termination Proofs for Bit-Vector Programs}

@@

To evaluate our algorithm, we implemented two tools: one to generate a
termination specification from a C program, and one to synthesise a proof
from the specification.  We ran the resulting termination prover on 47
benchmarks taken from the literature and SV-COMP'15~\cite{svcomp}.  To
provide a comparison point, we also ran {\sc ARMC}~\cite{armc-website} on
the same benchmarks.  Each tool was given a time limit of $180\,s$, and was
run on an unloaded 8-core 3.07\,GHz Xeon X5667 with 50\,GB of RAM.  The
results of these experiments are shown in Figure~\ref{fig:experiments}.

>>>>

\title{Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs}

@@

To evaluate our algorithm, we implemented two tools: one to generate a
termination specification from a C program, and one to synthesise a proof
from the specification.  We ran the resulting termination prover on 47
benchmarks taken from the literature and SV-COMP'15~\cite{svcomp15}.  To
provide a comparison point, we also ran {\sc ARMC}~\cite{armc-website} on
the same benchmarks.  Each tool was given a time limit of $180\,s$, and was
run on an unloaded 8-core 3.07\,GHz Xeon X5667 with 50\,GB of RAM.  The
results of these experiments are shown in Figure~\ref{fig:experiments}.
